Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-19 latex/article.tex
wip

>>>>

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to only
subdivide cells within the field of view.
